Storm Data Analysis - Week 4

### 2021-03-25 Manuscript.Rmd
Final plot (total dmg)

The choice of the fourteen categories was arbitrary, based on observation of event types appearing in the selected data. There are limitations to this approach, namely: events belonging to more than one category; and likely oversight of extremely rare events.

@@

# Create plot data, use dtplyr for speed and convenience
pdata <- lazy_dt(sel_data2)

>>>>

The choice of the fourteen categories was arbitrary, based on observation of event types appearing in the selected data. There are limitations to this approach, namely: events belonging to more than one category; and possible oversight of extremely rare events.

@@

# Make a copy of data to be sorted by damage total, descending, for use in
# damage-related plots.
dmgdata <- sel_data2 %>%
    group_by(event2) %>%
    summarise(total_dmg = sum(total_dmg)) %>%
    mutate(event2 = as.character(event2)) %>%
    arrange(desc(total_dmg)) %>%
    as_tibble()

dmgdata %>%
    ggplot(aes(
        x = reorder(event2, -total_dmg),
        y = total_dmg)) +
    geom_col() +
    scale_y_continuous(
        labels = scales::label_dollar(prefix = NULL,
                                      scale = 1e-9,
                                      largest_with_cents = 1),
        name = "Total estimated damages caused\n(in billions of dollars)\n"
    ) + 
    scale_x_discrete("\nWeather event category (1950–2013)") +
    coord_cartesian(ylim = c(0, 5e10)) +
    theme_classic()
